\phantomsection
\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}
The overall goal of this project is to create a device capable of generating detailed maps and imagery of an area in real-time. This device will rely on an FPGA, and will use image processing algorithms capable of detecting, localizing, and tracking human beings. The device will gather imagery from the visual light and infrared-spectrums, as well as localization data and distance measurements from an IMU and a rangefinder. Along with gathering and processing data, the device will also serve as a long-range wireless access point, and will be able to transmit all generated maps and imagery in real-time. A major deliverable of this project is that the transmitted data will be fully processed, allowing it to be viewed remotely on less-powerful, mobile devices.
\par
This device will be especially useful for first responders. It is intended to be mounted on a small remote control vehicle, allowing any connected user to wirelessly traverse dangerous and remote locations in search of people in need. Since this device transmits data in real-time, it will be able to provide first responders with an accurate representation of not only a 2-D floor plan of an area such as a building, but also where any people are located. An anticipated use of this device would be in the event of a building in danger of collapsing. Since it would be dangerous to physically enter the building, first responders could locate any people trapped inside and find the fastest route to them using the wirelessly transmitted floorplan. The first responders would also be aware of any dangers in their way by making use of the real-time augmented video stream. This video stream will consist of image data with overlaid with object indicators and location information on any human beings detected by the image processing algorithms.
 
