%https://www.sharelatex.com/learn/Bibliography_management_with_bibtex
\begin{thebibliography}{9}

\bibitem{adisBreakout}
Analog Devices, \textit{ADIS16IMU1/PCBZ Breakout Board Wiki-Guide}. 2016. Available from: \url{https://wiki.analog.com/resources/eval/user-guides/inertial-mems/imu/adis16imu1-pcb}.

\bibitem{adisDatasheet}
Analog Devices, \textit{Low Profile, Low Noise Six Degrees of Freedom Inertial Sensor}. Rev. C datasheet 2012. Available from: \url{http://www.analog.com/media/en/technical-documentation/data-sheets/ADIS16375.pdf}.

\bibitem{rs232}
ARC Electronics, \textit{RS232 Data Interface}. Available from: \url{http://www.arcelect.com/rs232.htm}.

\bibitem{ascii}
ASCII Table, \textit{ASCII Table - ASCII Character Codes}. 2010. Available from: \url{http://www.asciitable.com}.

\bibitem{al422b}
Averlogic.
\textit{AL422B Data Sheets}. 2001.
Available from: \url{http://www.frc.ri.cmu.edu/projects/buzzard/mve/HWSpecs-1/Documentation/AL422B_Data_Sheets.pdf}.

\bibitem{zedboard_datasheet}
AVNET, \textit{ZedBoard Hadware User's Guide}. Version 2.2 datasheet, 2014.

\bibitem{collins}
Robert Collins, \textit{CSE/EE486 Computer Vision I Fall 2007 Lecture Notes}. Available from: \url{http://www.cse.psu.edu/~rtc12/CSE486/}.

\bibitem{davison}
Davison, A.J.,
\textit{Real-Time Simultaneous Localisation and Mapping with a Single Camera}. 
IEEE Computer Vision, 2003. 2(1).

\bibitem{pmodnav_ref}
Digilent. \textit{Pmod NAV}. Available from: \url{https://reference.digilentinc.com/reference/pmod/pmodnav/start}.

\bibitem{armqp}
Dresser, L.H., A.W., \textit{Accelerating Augmented Reality Video Processing with FPGAs}. 2016. Available from: \url{https://www.wpi.edu/Pubs/E-project/Available/E-project-042716-172155/unrestricted/armqp-final-report.pdf}.

\bibitem{2sComp}
Thomas Finley. \textit{Two's Complement}. Available from: \url{http://www.tfinley.net/notes/cps104/twoscomp.html}. 2000.

\bibitem{rangefinder_photo}
Hokuyo Automatic Co. \textit{Scanning Laser Range Finder}. Available from: \url{https://www.hokuyo-aut.jp/02sensor/07scanner/urg_04lx.html}. 2009.

\bibitem{urg04lx_specifications}
Hokuyo Automatic Co. \textit{Scanning Laser Range Finder URG-04LX Specifications}. C-42-3389 datasheet, 2012.

\bibitem{urg04lx_datasheet}
Hokuyo Automatic Co. \textit{URG Series Communication Protocol Specification}. C-42-3320-A datasheet, 2012.

\bibitem{URGBenriStandard_ref}
Hokuyo Automatic Co. \textit{UrgBenri data viewing tool}. 2014. Available from: \url{https://www.hokuyo-aut.jp/02sensor/07scanner/download/data/UrgBenri.htm}.

\bibitem{livm34lp}
Leopard Imaging Inc.
\textit{LI-VM34LP Camera Board}. 2009.
Available from: \url{http://www.leopardimaging.com/uploads/li-vm34lp_v1.1.pdf}.

\bibitem{serveball}
\textit{Serveball}.
Available from: \url{http://www.serveball.com/}.

\bibitem{mattoccia}
Stefano Mattoccia, M.P.,
\textit{A passive RGBD sensor for accurate and real-time depth sensing self-contained into an FPGA}.
in \textit{International Conference on Distributed Smart Cameras}. 2015.

\bibitem{lps25hd}
STMicroelectronics. \textit{LPS25HD MEMS pressure sensor}. DocID027112 Rev 4 datasheet, 2016.

\bibitem{lsm9ds1}
STMicroelectronics. \textit{LSM9DS1 iNEMO inertial module: 3D accelerometer, 3D gyroscope, 3D magnetometer}. DocID025715 Rev 3 datasheet, 2015.

\bibitem{ttl}
Sparkfun Electronics, \textit{RS-232 vs. TTL Serial Communication}. 2010. Available from: \url{https://www.sparkfun.com/tutorials/215}.

\bibitem{mattoccia_slides}
Stefano Mattoccia, \textit{Stereo Vision}. Available from: \url{http://www.slideshare.net/DngNguyn43/stereo-vision-42147593}.

\bibitem{mccormick}
Chris McCormick, \textit{Stereo Vision Tutorial  - Part 1}. Available from: \url{http://mccormickml.com/2014/01/10/stereo-vision-tutorial-part-i/}.

\bibitem{mt9v032}
On Semiconductor. 
\textit{MT9V032: 1/3-Inch Wide-VGA CMOS Digital Image Sensor}. 2015. 
Available from: \url{http://www.onsemi.com/pub_link/Collateral/MT9V032-D.PDF}.

\bibitem{mt9v034}
On Semiconductor. 
\textit{MT9V034: 1/3-Inch Wide-VGA CMOS Digital Image Sensor}. 2015. 
Available from: \url{http://www.onsemi.com/pub_link/Collateral/MT9V034-D.PDF}.

\bibitem{porikli}
Fatih Porikli, O.T.,
\textit{Human Body Tracking by Adaptive Background Models and Mean-Shift Analysis}.
in \textit{IEEE International Workshop on Performance Evaluation of Tracking and Surveillance}. 2003.

\bibitem{thrun}
Sebastian Thrun, D.H., David Ferguson, Michael Montemerlo, Rudolph Triebel, and C.B. Wolfram Burgard, Zachary Omohundro, Scott Thayer, William Whittaker.
\textit{A System for Volumetric Robotic Mapping of Abandoned Mines}. 
in \textit{IEEE International Conference on Robotics and Automation}. 2003.

\bibitem{usb-otg}
Wikipedia. \textit{USB On-The-Go}. 2017. Available from: \url{https://en.wikipedia.org/wiki/USB_On-The-Go}.

\bibitem{polar_coordinates}
Wolfram MathWorld. \textit{Polar Coordinates}. 2016. Available from: \url{http://mathworld.wolfram.com/PolarCoordinates.html}.

\bibitem{zedboardErrata}
Xilinx. \textit{AR\# 47511: Zynq-7000 AP SoC, SPI - In Master Mode on MIO, the SPI Controller Resets Itself when the SS0 Signal Asserts}. 2013. Available from: \url{http://www.xilinx.com/support/answers/47511.html}.

\bibitem{microblaze}
Xilinx. \textit{MicroBlaze Soft Processor Core}. 2015. Available from: \url{https://www.xilinx.com/products/design-tools/microblaze.html}.

\bibitem{zynq7ps}
Xilinx. \textit{Processing System 7 v5.5 LogiCORE IP Product Guide}. in \textit{Vivado Design Suite}. PG082 datasheet, 2015.

\bibitem{zynq7bram}
Xilinx. \textit{7 Series FPGAs Memory Resources User Guide}. 2016. Available from: \url{https://www.xilinx.com/support/documentation/user_guides/ug473_7Series_Memory_Resources.pdf}.

\end{thebibliography}

% include in ToC - must be after refs for correct page link from hyper
\addcontentsline{toc}{section}{References}



