\subsection{Useful Resources}
This section is intended to serve as complete compilation of all resources gathered throughout D Term 2016 that we believe will be useful as we begin to work on the methodology portion of our project.

\begin{itemize}
  \item Strother, Daniel. 2011. "Open-Source FPGA Stereo Vision Core Released." \path{https://danstrother.com/2011/06/10/fpga-stereo-vision-core-released/}.
  
  \item Field, Mike. 2013. "Zedboard OV7670." \path{http://hamsterworks.co.nz/mediawiki/index.php/Zedboard_OV7670}.
  
  \item "OV7670/OV7671 CMOS VGA CameraChip Implementation Guide." \path{https://www.fer.unizg.hr/_download/repository/OV7670new.pdf}.
  
  \item "MIPI CSI2-to-CMOS Parallel Sensor Bridge - Lattice Semiconductor." \path{http://www.latticesemi.com/~/media/LatticeSemi/Documents/ReferenceDesigns/JM/MIPICSI2to CMOSParallelSensorBridgeDocumentation.pdf?document_id=50533}.
  
  \item "OmniVision Serial Camera Control Bus (SCCB) Functional Specification." \path{http://www.ovt.com/download_document.php?type=document&DID=63"}.
  
  \item Morvan, Yannick. "Multiple-View Depth Estimation." \path{http://www.epixea.com/research/multi-view-coding-thesisse15.html}.
  
  \item MathWorks. "Depth Estimation From Stereo Video." \path{http://www.mathworks.com/help/vision/examples/depth-estimation-from-stereo-video.html}.
  
  \item Stefano Mattoccia, Matteo Poggi. 2015. "A passive RGBD sensor for accurate and real-time depth sensing self-contained into an FPGA". International Conference on Distributed Smart Cameras.
  
  \item Mattoccia, Stefano. 2013. "Stereo Vision: Algorithms and Applications." \path{http://www.slideshare.net/DngNguyn43/stereo-vision-42147593}.
  
  \item Szeliski, Richard. 2010. Computer Vision: Algorithms and Applications. New York: Springer.
  
  \item Beau Tippets, Dah Jye Lee, Kirt Lillywhite, James Archibald. 2013. "Review of Stereo Vision Algorithms and Their Suitability for Resource-Limited Systems." Journal of Real-Time Image Processing 11 (1). doi: 10.1007/s11554-012-0313-2.
  
  \item Jouni Rantakokko, Joakim Rydell, Peter Stromback, Peter Handel, Jonas Callmer, David Tornqvist, Fredrik Gustafsson, Magnus Jobs, Mathias Gruden. 2011. "Accurate and Reliable Soldier and First Responder Indoor Positioning: Multisensor Systems and Cooperative Localization." IEEE Wireless Communications 18 (2):10-18. doi: 10.1109/MWC.2011.5751291.
  
  \item Davison, Andrew J. 2003. "Real-Time Simultaneous Localisation and Mapping with a Single Camera."  IEEE Computer Vision 2 (1). doi: 10.1109/ICCV.2003.1238654.
  
  \item Fatih Porikli, Oncel Tuzel. 2003. "Human Body Tracking by Adaptive Background Models and Mean-Shift Analysis." IEEE International Workshop on Performance Evaluation of Tracking and Surveillance.
  
  \item Giovanni Pintore, Enrico Gobbetti. "Effective mobile mapping of multi-room indoor structures."  The Visual Computer 30 (6):707-716. doi: 10.1007/s00371-014-0947-0.
  
  \item "iRobot 110 FirstLook." iRobot. \path{http://www.irobot.com/$~$/media/Files/Robots/Defense/FirstLook/iRobot-110-FirstLook-Specs.pdf}.

\end{itemize}
